A Simple Ratio for Estimating the Effective Reproduction Value of an Epidemic

### 2021-01-16 docs/manuscript/manuscript.Rmd
moved variable

```{r sim-results, fig.cap = '(ref:sim-results-cap)'}

# Descriptive Statistics
N = simulation_parameters$initial_state_values %>% sum()
error_median = with(rt_estimates, median(abs(rt.simple_mean_error), na.rm = T)) %>% signif(digits = 2)
error_quantile_975 = with(rt_estimates, quantile(abs(rt.simple_mean_error), 0.975, na.rm = T)) %>% signif(digits = 2) %>% format(scientific = F)
error_quantile_025 = with(rt_estimates, quantile(abs(rt.simple_mean_error), 0.025, na.rm = T)) %>% signif(digits = 2) %>% format(scientific = F)

# 
rt_estimates_error_summary <- rt_estimates %>%
  filter(time > 14) %>%
  group_by(simulation_run) %>%
  summarise(dm_test = list(dm.test(rt.simple_mean_error, rt.cori_mean_error)))

# Plots
panel_A <- rt_estimates %>%
  filter(simulation_run == 66) %>%
  create_estimate_plot()

>>>>

```{r sim-results, fig.cap = '(ref:sim-results-cap)'}
# Plots
panel_A <- rt_estimates %>%
  filter(simulation_run == 66) %>%
  create_estimate_plot()
